\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

% adjust the page margins
\usepackage[scale=0.90]{geometry}
\linespread{0.90} 
% personal data
\name{Mukesh Tiwari}{}
\email{mt883@cam.ac.uk}
\phone[mobile]{+447824648138}               
\address{Cambridge, United Kingdom}


\begin{document}

\recipient{To}{The Hiring Committee \\ Department of Engineering, 
  University of Cambridge, Cambridge}
\date{}
\opening{\textbf{Application for the post of Assistant Professor in Innovative Computational Methods}}
\closing{Your Sincerly, \vspace{-1em}}



\makelettertitle


Dear Hiring Committee, 
\\
%references such as what and how you got this information
\vspace{1em}
My name is Mukesh Tiwari and  I am a senior research associate at 
the University of Cambridge, Cambridge, UK. 
I am writing to apply
for the job \textbf{Assistant Professor in Innovative Computational Methods}. 
I have an extensive experience in
formal verification (Coq theorem prover), security research (Cryptography), 
social choice theory (voting), and networking, 
and I find the Engineering Department, University of Cambridge is 
a perfect place to continue my research and expand my horizons in other areas,  
including autonomous systems, AI, safety-critical machine learning, etc.



\vspace{0.5cm}
Engineering Department, University of Cambridge has many projects, e.g., AI, safety-critical 
machine learning, climate research,  etc., that touch many common people's life.
My philosophy is that we should mathematically verify the software programs 
that affect the life of common people, and therefore we, me and 
Cambridge Engineering Department, complement each other.
I can strengthen the Cambridge Engineering 
Department in mathematically verified AI, safety-critical machine learning, 
climate research, while 
at the same time Cambridge Engineering Department offers me leading experts 
and projects  in safety-critical machine learning, AI, and climate research
that affect the life of common people. Together, with our combined expertise, 
we can make the software used in public domain more trustworthy and 
a meaningful impact. 

After looking at the profiles at Information Engineering group, I find that I can 
collaborate with everyone, but due to lack of space\footnote{1 page cover letter}  
I am listing the people, close to my research, whom I can collaborate 
immediately. 

\begin{itemize}
  \item Zoubin Ghahramani: we can work on social choice theory. His work 
 on partial ranking is very similar to voting. Combining preferences 
 are key step in voting (electing a winner), 
 and I am very interested in learning his work on extend kernel
 methods for complete rankings to partial rankings to see how it 
 can be used in voting. In addition, we can collaborate 
 on formally verified functional programming 
 for Bayesian modelling and inference in Coq and Lean
 theorem prover.

\item Simon Godsill: we can work on formal underpinning 
  of Bayesian Computational Methods. We can start with formalisation of 
  a probability distribution\footnote{I have already done some 
  work in discrete probability distribution 
  \url{https://github.com/mukeshtiwari/Dlog-zkp/blob/main/src/Distr.v}}
  and then formalise \textit{Bayesian Computational Methods}. I would also 
  like to work on formal underpinning of computer vision, given 
  that it is used in autonomous cars, but it is a very difficult problem 
  (a perfect research problem).
\item Dr Adrian Weller: we can collaborate on trustworthy AI, using logic. 
  As a first step, we can work on a formal meaning of \textit{trustworthyness}
  and then we can show that our AI system follows our definition of textit{trustworthyness}.
  I am very interested in working with him because he works 
  on many topics, e.g.,  explainability, fairness, robustness, 
  scalability, privacy, safety, ethics and finance, which I find 
  very interesting and impactful.

\end{itemize}

As an independent researcher, I will seek for funding from the UK national funding 
agencies and companies that are pushing machine learning in public domain. 
My formal verification expertise, in conjunction with machine learning 
experts at Cambridge Engineering Department, makes me an unique candidate 
to solve many of the challenging problems in safety-critical machine 
learning domain.

I would like to emphasize that my research had been severely 
impacted by Melbourne lockdown and therefore I was not very productive 
in year 2020 and 2021, but I have several works, 5 projects, now in publication 
pipeline, and 3 projects are ongoing.  In addition, it takes almost 1.5 
year to formalise anything  substantial and most of the time is/are? 
taken by the proofs. 


\vspace{0.5cm}
I look forward to hearing from you. Let me know if you have any 
questions. \\
 

\vspace{0.5cm}


\makeletterclosing

\end{document}

