%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

% adjust the page margins
\usepackage[scale=0.90]{geometry}

% personal data
\name{Mukesh Tiwari}{}
\email{mt883@cam.ac.uk}
\phone[mobile]{+447824648138}               
\address{Cambridge, United Kingdom}


\begin{document}

\recipient{To}{The Hiring Committee, \\
Eindhoven University of Technology,\\ Netherlands}
\date{}
\opening{\textbf{Application for the post of Assistant Professor- Mathematics and Computer Science}}

\closing{Your Sincerly, \vspace{-1em}}



\makelettertitle



Dear Hiring Committee, 
\\
%references such as what and how you got this information
\vspace{1em}
I am writing to apply
for the Lecture job in Assistant Professor- Mathematics and Computer Science.
I have extensive research experience in
(election) software security, theorem proving (Coq theorem prover), cryptography,  
and social choice theory. 
I have a PhD from the Australian National University, Canberra, Australia
and Currently, I am working as a Senior Research Fellow at the University of 
Cambridge. Before moving to Cambridge, I was a 
research fellow at the University of Melbourne. 


My research --constructing mathematically proven correct software program-- 
perfectly aligns with your department. I can collaborate with many researchers 
working at Coding Theory and Cryptology group on diverse set of projects because of 
my expertise in theorem proving (Coq), e.g., 
Berry Schoenmakers on formalising voting projects, Tanja Lange  and Andreas H\"{u}lsing 
on formalising post-quantum cryptography for voting,  Sven Sch\"{a}ge on 
formalising cryptographic protocols, etc. In addtion, as an assistant professor at the 
Eindhoven University of Technology, 
I would like to expand my research area into other areas of 
security and formal verification, e.g., domain specific language to reason about 
functional correctness and security properties --from computational complexity perspective-- of 
cryptographic algorithms, anonymous communication, blockchain, zkSNARK,  
information flow security, computational complexity of social choice methods, 
etc. My research has been published in top-tier conferences, e.g., Interactive Theorem Proving (ITP), 
Computer and Communications Security (CCS), USENIX security, Electronic Voting (EVote), 
International Conference on Cryptology in India (IndoCrypt),
and some (finished) works have been submitted to CCS and SIGCOMM. 
All my research work has been formalised in the Coq theorem prover. 


\vspace{0.5cm}



I look forward to hearing from you. Please let me know if you have any questions. \\
 

\vspace{0.5cm}


\makeletterclosing

\end{document}

