



%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

% adjust the page margins
\usepackage[scale=0.90]{geometry}

% personal data
\name{Mukesh Tiwari}{}
\email{mt883@cam.ac.uk}
\phone[mobile]{+447824648138}               
\address{Cambridge, United Kingdom}


\begin{document}

\recipient{To}{Andy Tripathi, \\
Deputy Chief Information Officer, Canberra}
\date{}
\opening{\textbf{Application for the Director, Cyber Security}}
\closing{Your Sincerly, \vspace{-1em}}



\makelettertitle

Dear Andy Tripathi, 

I am writing to apply
for the \textbf{Director, Cyber Security} job. 
I have extensive research and practical experience in cyber security, 
theorem proving (Coq theorem prover), (election) software security, cryptography,  
and social choice theory. My PhD goal was to develop an unhackable 
electronic vote-counting software by using mathematical logic.
In the process, I understood the security requirement of 
the vote-counting software and then came up with a threat model under 
which it could be operated. In addition,  my research is highly 
relevant to a democracy, e.g., Canberra that conducts 
an election using software programs. I have developed many 
mathematically proven correct (unhackable)  
solutions that address the problems, pointed by researchers, 
of e-voting software programs, e.g.,
I have developed a mathematically proven correct software for
for Swiss elections, including the threat model.
I have a PhD from the Australian National University, Canberra, Australia,
and currently, I am working as a senior Research Fellow at the University of 
Cambridge. Before moving to Cambridge, I was a 
research fellow at the University of Melbourne, Australia.


In addition to my advanced degree, I also have 3 
years of experience in the field of information security 
and risk management as a contractor for government of India. 
My role was to understand and access the cyber risks and 
come with a potential solution and countermeasures, in conjunction with 
other domain experts, to mitigate them.
As a holder of a PhD in cyber security, I have a 
strong foundation 
in software security and threat modelling, which I believe would make me a 
valuable asset for this position.


I am excited about the opportunity to join ACT government and use my skills 
and expertise to protect the business from cyber threats. 
Thank you for considering my application. I look forward to discussing 
the \textbf{Director, Cyber Security} role further and how I 
can contribute to the 
success of your team. Please let me know if you have any questions. \\
 

\vspace{0.5cm}


\makeletterclosing

\end{document}











