



%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

% adjust the page margins
\usepackage[scale=0.90]{geometry}

% personal data
\name{Mukesh Tiwari}{}
\email{mt883@cam.ac.uk}
\phone[mobile]{+447824648138}               
\address{Cambridge, United Kingdom}


\begin{document}

\recipient{To}{The Hiring Committee, \\
University of Adelaide, Adelaide, Australia}
\date{}
\opening{\textbf{Selection Criteria Address for the Lecturer 
in Computer Science}}
\closing{Your Sincerly, \vspace{-1em}}



\makelettertitle

Dear Hiring Committee, 

I have a PhD in computer science from the Australian National University, 
Canberra and two postdoc research experience from the University of 
Melbourne and the University of Cambridge. My research 
mainly focuses on making software unhackable by eliminating all 
the bugs using mathematical logic. I have led various successful projects
in my PhD and postdocs, e.g., differential privacy machine learning, 
homomorphic vote counting, mix-networks, etc.  My research has been 
published in top security and theorem proving conferences, e.g., 
Interactive Theorem Proving (ITP), 
Computer and Communications Security (CCS), USENIX, Electronic Voting (EVote), 
International Conference on Cryptology in India (IndoCrypt),
and some (finished) works have been submitted to CAV and IEEE Security and Privacy. 

In addition, I have extensive teaching experience. I have taught in 
a technical school in India as an assistant professor and tutored 
many courses in the Australian National University as a senior tutor.
In addition, at the University of Cambridge I have supervised bachelors and masters students.
I have also contributed to many international conferences 
as a reviewer and artefact evaluation committee member.



I look forward to hearing from you. Please let me know if you have any questions. \\
 


\makeletterclosing

\end{document}











