%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

% adjust the page margins
\usepackage[scale=0.90]{geometry}

% personal data
\name{Mukesh Tiwari}{}
\email{mt883@cam.ac.uk}
\phone[mobile]{+447824648138}               
\address{Cambridge, United Kingdom}


\begin{document}

\recipient{To}{The Hiring Committee, \\
CentraleSup\'elec (Rennes campus), France}
\date{}
\opening{\textbf{Application for the post of Assistant Professor in Computer Science}}

\closing{Your Sincerly, \vspace{-1em}}



\makelettertitle



Dear Hiring Committee, 
\\
%references such as what and how you got this information
\vspace{1em}
I am writing to apply
for the Assistant Professor job in Computer Science.
I have extensive research experience in
(election) software security, theorem proving (Coq theorem prover), cryptography,  
and social choice theory. 
I have a PhD from the Australian National University, Canberra, Australia
and Currently, I am working as a Senior Research Fellow at the University of 
Cambridge. Before moving to Cambridge, I was a 
research fellow at the University of Melbourne. 


My research --constructing mathematically proven correct software program-- 
perfectly aligns with one of your group's mission: formal methods for security. 
Based on my formal verification background, 
I can immediately contribute to the ongoing efforts to specify and verify 
microarchitectural level properties and software/hardware 
security mechanism of \textbf{CIDRE} team.  
In addition, as an assistant professor at the CentraleSup\'elec, 
I would like to expand my research area into other areas, e.g., 
network security, malware analyses, embedded 
system security, anonymous communication, blockchain, zkSNARK,
and information flow security. My research has been published in top-tier 
conferences, e.g., Interactive Theorem Proving (ITP), 
Computer and Communications Security (CCS), USENIX security, Electronic Voting (EVote), 
International Conference on Cryptology in India (IndoCrypt),
and some (finished) works have been submitted to CCS and SIGCOMM. 
All my research work has been formalised in the Coq theorem prover. 




\vspace{0.5cm}



I look forward to hearing from you. Please let me know if you have any questions. \\
 

\vspace{0.5cm}


\makeletterclosing

\end{document}

